\documentclass[12pt]{article}
\pagestyle{empty}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{latexsym, epsfig, ulem, cancel, multicol, hyperref}
\usepackage{graphicx, tikz, subfigure,pgfplots}
\usepackage[margin=1in]{geometry}
\setlength{\parindent}{0pt}
\usepackage{multirow}
\usepackage{mathtools}


\newcommand{\R}{\mathbb{R}}
\newcommand{\dydx}{\frac{dy}{dx}}
\usepackage{verbatim}
\usepackage{tikz}
\usepackage{pgfplots}

\newcommand{\wsnumber}{1}
\newcommand{\wstopic}{Vectors}
\pgfplotsset{
    every linear axis/.append style={
       axis x line=center,
       axis y line=center,
       xlabel={$x$},
       ylabel={$y$}
    },
    every axis plot/.append style={thick,mark=none}
}
\tikzset{
    point/.style={circle,draw,fill,minimum width=0.3ex,inner sep=0pt,outer sep=0pt},
    every label/.append style={black}
}


\usepackage[margin=1in]{geometry}
\usepackage{amsmath, amssymb, amsthm, graphicx, hyperref}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{multirow, multicol}
\usepackage{tikz}
\pagestyle{fancy}
\fancyhead[RO]{Dennis Li}
\fancyhead[LO]{Summer 6W2 2024 MA-UY 2314}
\usepackage{comment}
\newif\ifshow
\showfalse

\ifshow
  \newenvironment{solution}{\textbf{Solution.}}{}
\else
  \excludecomment{solution}
\fi

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\usepackage{comment}


\newtheorem*{remark}{Remark}


\begin{document}

\begin{center}
\ifshow
  \textbf{\Large Homework 0 Solution}\\
\else
  \textbf{\Large Homework 0}\\
\fi
Due: Tuesday July 9\\via Gradescope\\
\end{center}

\hrule

\vspace{0.2cm}

\begin{enumerate}[$\bullet$]  
\item Late homework is not accepted.  Lateness due to technical issues will not be excused.  
\end{enumerate}

\hrule

\vspace{0.5cm}


Please give a brief response to each of the following questions or instructions.
\begin{enumerate}
\item
    \begin{enumerate}[(a)]
        \item Write your Name and Your NYU NetID \\
        \\Name: Dennis Li (Formally \textit{Zhuobin Li})\\
        NetID: zl2941\\
        \item What is your major or intended major?\\
        \\I am a Applied Physics major.\\
        \item What was your most recent math course before this one and when did you take it?\\
        \\MA-UY-3113 Complex Variables and Linear Algebra, Spring 2024\\
    \end{enumerate}
\item
    \begin{enumerate}[(a)]
        \item Why are you taking this course? \\
        \\To learn how to derive and organize a proof using mathematical language, or just learn how math proofs are done to help with logical skills. \\
        \item What do you hope to learn or to gain from this course? \\
        \\A method of expressing my arguments in a mathematically rigorous way. \\
        \item How did the first week of our course go for you?\\
        \\It is only one class, which is quite fun and engaging, and I have heard many great things about professor Cereste so I am excited for whats coming.  \\
    \end{enumerate}

\item Write out the following statement. Include your name and signature where indicated.\\

\textit{I, \textbf{Dennis Li}, have carefully read the syllabus, as briefly reviewed in our first class meeting, and I understand the structure of the course as stated in the syllabus, including the homework and exam structure. If and when I have a question about the course structure, I will read the syllabus prior to asking the professor a question.}\\ \\
\textit{Dennis Li}

\end{enumerate}



\end{document}